A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2015-11-25 docs/discussion_v3.02.tex
Small changes in Discussion.

\citet{Ferreras} found a relation between the central stellar velocity dispersion $\sigma_0$ in early-type galaxies and the IMF slope $x$; a higher $\sigma_0$ suggests a more bottom-heavy IMF. For a unimodal (Salpeter-like) IMF and $\sigma_0 \simeq 200~\text{km s}^{-1}$ in J1331 (see Figure \ref{fig:kinematics}) they predict $x \approx 2.33$, which is close to the standard Salpeter slope, also supported by \citet{2014MNRAS.438.1483S}. When assuming a bi-modal (Kroupa-equivalent-like) IMF, \citet{Ferreras} predict $x \approx 2.85$ for J1331's central velocity dispersion. This is more bottom-heavy than the standard \citet{2002Sci...295...82K} IMF. Overall, the central velocity dispersion suggests a rather bottom-heavy IMF in J1331's bulge and therefore large stellar mass-to-light ratio. \citet{SWELLSI} estimated J1331's stellar bulge mass given a Salpeter IMF and measured the I-band AB magnitude of the bulge. Transformed to a stellar I-band mass-to-light ratio their results would correspond to $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ (see Table \ref{tab:previousresults}).

We compare our results from Section \ref{sec:results_JAM_NFW} with the study by \citet{SWELLSV}: They found that the bulge of J1331 has an IMF \emph{more} bottom-heavy than the Salpeter IMF from fitting a NFW halo to (1) the Einstein mass and (2) gas kinematics at larger radii $\gtrsim 8''$. In Section we fitted a mass model with NFW halo to (1) the Einstein mass and (2) stellar kinematics within $\sim 3.5''$. Our best fit $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}) indicates a \emph{less} bottom-heavy IMF than the Salpeter IMF. \cite{SWELLSV} found systematically lower NFW halo masses ($v_\text{circ,halo}(5'') \sim 120~\text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ,halo}(5'') \sim 200~\text{km s}^{-1}$).

We compare our result from Section \ref{sec:results_JAM_SB} with the findings from \citet{SWELLSI}: We created a dynamical model from only the surface brightness distribution and an increasing mass-to-light ratio profile without additional DM halo. We found that such a model would be perfectly consistent with the Einstein mass and predict a total $\Upsilon_\text{I,tot}(R'\sim0) = 2.53$ in the very center of J1331. This is close to the stellar $\Upsilon_\text{I,*}^\text{Chabrier} = 2.5 \pm 0.6$ based on the estimates by \citet{SWELLSI} for the bulge stellar mass using the Chabrier IMF , i.e., less bottom-heavy (more bluish) population.

@@

>>>>

\citet{Ferreras} found a relation between the central stellar velocity dispersion $\sigma_0$ in early-type galaxies and the IMF slope $x$; a higher $\sigma_0$ suggests a more bottom-heavy IMF. For a unimodal (Salpeter-like) IMF and $\sigma_0 \simeq 200~\text{km s}^{-1}$ in J1331 (see Figure \ref{fig:kinematics}) they predict $x \approx 2.33$, which is close to the standard Salpeter slope, also supported by \citet{2014MNRAS.438.1483S}. When assuming a bi-modal (Kroupa-equivalent-like) IMF, \citet{Ferreras} predict $x \approx 2.85$ for J1331's central velocity dispersion. This is more bottom-heavy than the standard \citet{2002Sci...295...82K} IMF. Overall, the central velocity dispersion suggests a rather bottom-heavy IMF in J1331's bulge and therefore large stellar mass-to-light ratio.

\citet{SWELLSI} estimated J1331's stellar bulge mass given a Salpeter IMF and measured the I-band AB magnitude of the bulge. Transformed to a stellar I-band mass-to-light ratio, their results would correspond to $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ (see Table \ref{tab:previousresults}). This is not too far from $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ (see Table \Wilma{[TO DO]}), which we found when including a NFW halo in the JAM modelling.

When \citet{SWELLSI} assumed a Chabrier IMF, their result translates to $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$ (see Table \ref{tab:previousresults}). In Section \ref{sec:results_JAM_SB} we created a dynamical model from only the surface brightness distribution and an increasing mass-to-light ratio profile without additional DM halo. We found that such a model would be perfectly consistent with the Einstein mass, predict a total $\Upsilon_\text{I,tot}(R'\sim0) = 2.53$---being consistent with the Chabrier IMF estimate by \citet{SWELLSI}---and rise quickly to $\Upsilon_\text{I,tot}(R'\gtrsim R_\text{ein}) \gtrsim 6$.

We also compare our results from Section \ref{sec:results_JAM_NFW} with the study by \citet{SWELLSV}. They found that the bulge of J1331 has an IMF \emph{more} bottom-heavy than the Salpeter IMF from fitting a NFW halo to (1) the Einstein mass and (2) gas kinematics at larger radii $\gtrsim 8''$. In Section we fitted a mass model with NFW halo to (1) the Einstein mass and (2) stellar kinematics within $\sim 3.5''$. Our best fit $\Upsilon_\text{I,*} = 4.2 \pm 0.2$ (see Table \ref{tab:modelB4_bestfit}) indicates a \emph{less} bottom-heavy IMF than the Salpeter IMF. \cite{SWELLSV} found systematically lower NFW halo masses ($v_\text{circ,halo}(5'') \sim 120~\text{km s}^{-1}$ according to their Figure 2) than we did ($v_\text{circ,halo}(5'') \sim 200~\text{km s}^{-1}$).

@@

This could indicate that there might be a less bottom-heavy, more bluish population, with an IMF close to the Chabrier IMF, in the very center of J1331.
